---
title: "Customer Segmentation and Life Time Value for Flash Deal Site "
author: "Steffen Hartleib"
date: "`r format(Sys.Date())`"
output: 
  html_document:
    keep_md: TRUE
---

### The Data Set

##### Online purchase data from 2010 to 2016
##### 553087 observations (line items), 19 variables

### Questions
##### 1. Which customer segments are driving revenue? 
##### 2. What is the  average life time value of a customer?

***

### Let's look at year over year revenue and customer trends

```{r, echo = FALSE, eval = TRUE,  message=FALSE , warning = FALSE}

# load packages
library(dplyr)
library(reshape2)
library(ggplot2)
library(knitr)
library(RMySQL)
options(scipen=10000)

# Read data -------------------------------------------------------------------------------------

mydb <-  dbConnect(MySQL(), 
                   user = Sys.getenv('mysql_user'),
                   password = Sys.getenv('mysql_pw'),
                   dbname = Sys.getenv('db_name'),
                   host = Sys.getenv('db_host'))
rs <- dbSendQuery(mydb, 'select* from lineItems where store_id in (5693042, 1)')
d <- fetch(rs, n = -1)
dbDisconnect(mydb)


# Group by order to calcluate Product Revenue (Rev) net of Discounts, which are on an order level

data = group_by(d,Order_ID, Email, Created_at, Discount_Amount)%>%
               summarize(Prod_Rev = round(sum(Lineitem_quantity * Lineitem_price),2))%>%
               mutate(Rev = Prod_Rev - Discount_Amount)

# Select columns, format date, add purchase year and recency -------------------- 

data_1 = data[,c('Email','Rev','Created_at')]
colnames(data_1) = c('email','amount','purchase_date')
data_1$purchase_date = as.Date(data_1$purchase_date, '%Y-%m-%d')
data_1$purchase_year = as.numeric(format(data_1$purchase_date,'%Y'))
data_1$days_since = as.numeric(difftime(time1 = '2017-02-02',
                                        time2 = data_1$purchase_date,
                                        units ='days'))


# summary statistics------------------------------------------------------------------------------------

yearly_rev = select(data_1, purchase_year, amount, email)%>%
                group_by(purchase_year)%>%
                summarize(rev = round(sum(amount),0),
                          cust = n_distinct(email),
                          pur = n(),
                          avg_price = round(mean(amount),0),
                          avg_rev_cust = round(sum(amount)/length(unique(email)),0),
                          avg_no_purch_cust = round(n()/length(unique(email)),2))

ggplot(yearly_rev, aes(purchase_year, rev)) + geom_bar(stat= "identity") + 
        ggtitle("Yearly Revenue:\n") + ylab("$ Revenue") + xlab("Year")

ggplot(yearly_rev, aes(purchase_year, cust)) + geom_bar(stat= "identity") + 
        ggtitle("Number of Unique Customers:\n") + ylab("No. of active customers") + xlab("Year")

ggplot(yearly_rev, aes(purchase_year, avg_price)) + geom_bar(stat= "identity") + ggtitle("Average Order Value:\n ") + ylab("Avg. Order Value") +  xlab("Year")

ggplot(yearly_rev, aes(purchase_year, avg_rev_cust)) + geom_bar(stat= "identity") + ggtitle("Average Revenue per Customer:\n") + ylab("Avg. Rev. per customer") + xlab('Year')

ggplot(yearly_rev, aes(purchase_year, avg_no_purch_cust)) + geom_bar(stat= "identity") + ggtitle('Average Number of Orders per Customer:\n') + ylab("Avg. no of orders per customer")
```


##### In 2016 the number of customers increased significantly. But Total Revenue rose only slightly. Because, on average, customer placed fewer orders and spent less per order. This is pattern is typical for customer acquistion campaigns driven by discounts. The challenge will be to convert these new customers from bargain shoppers to valuable long term customers.
##### Let's segement the customers to see what's behind these trends.
&nbsp;


***

### Simple Customer Segmentation by Recency, Frequency and Monetary Value (RFM) 
##### We need to calculate three variables per customer:
##### 1. Recency: Number of days since the last purchase
##### 2. Frequency:  Number of orders placed, life to date
##### 3. LTD Revenue: Product Revenue net of discounts life to date
&nbsp;

#### Here are the summary statistics of each variable: 




```{r, echo = FALSE , eval = TRUE, message=FALSE, warning = FALSE}

# Group by email for LTD values
customers_365 = select(data_1, email, amount, purchase_year,days_since)%>%
                      group_by(email)%>%
                      filter(amount > 0)%>%
                      summarize(avg_amount = mean(amount),
                           tl_rev = round(sum(amount),0),
                           recency = min(days_since),
                           first_purchase = max(days_since),
                           frequency = n())
#View(customers_last_yr)

# Get last year's revenue by customer
customer_rev_365 = select(data_1,email,amount,days_since)%>%
                        filter(days_since <= 365)%>%
                        group_by(email)%>%
                        summarize(Rev_365 = round(sum(amount),0))

customers_365 = merge(customers_365 ,customer_rev_365, all.x = TRUE, by = 'email')

customers_365$Rev_365[which(is.na(customers_365$Rev_365))] = 0

means = select(customers_365, avg_amount, tl_rev, recency, 
              first_purchase,frequency,Rev_365)%>%
              summarize_each(funs(mean))%>%
              summarize_each(funs(round))
      
mins = select(customers_365, avg_amount, tl_rev, recency, 
              first_purchase,frequency,Rev_365)%>%
              summarize_each(funs(min))%>%
              summarize_each(funs(round))

max = select(customers_365, avg_amount, tl_rev, recency, 
              first_purchase,frequency,Rev_365)%>%
              summarize_each(funs(max))%>%
              summarize_each(funs(round))


med = select(customers_365, avg_amount, tl_rev, recency, 
              first_purchase,frequency,Rev_365)%>%
              summarize_each(funs(median))%>%
              summarize_each(funs(round))


summary = rbind(prettyNum(round(mins),big.mark=","),
                prettyNum(round(means),big.mark=","),
                prettyNum(round(med),big.mark= ","),
                prettyNum(round(max),big.mark = ","))


row.names(summary) = c('Minimum','Average','Median','Max')
colnames(summary) = c("Avg. Purchase","LTD Revenue","Recency","Days since first purch.", "No of Purchases","Revenue 2015")

summary_df <- data.frame(summary)

summary_table <- select(summary_df, Recency, LTD.Revenue, No.of.Purchases)
summary_table

```

##### Look at LTD Revenue! The mean is over three times the median. And one customer spent over $200k. Clearly a few high rolers are pulling up the the average. (A bit like Bill Gates sitting down at your neighborhood bar...)
&nbsp;

***

### Let's define our customer segements as follows. I'm using round numbers since this is a managerial analysis.
 
Segment        | Recency                | LTD Revenue  
-------------  | ---------------------  | -------------  
 Active New    | 1st purchase last year | 
 Active Low    | purchase last year     | < $100
 Active Med    | purchase last year     | >= $100 & < $1000
 Activ High    | purchase last year     | > $1000
 Inactive Low  | no purchase last year  | < $100
 Inactive Med  | no purchase last year  | >= $100 & < $1000
 Inactive High | no purchase last year  | > $1000

&nbsp;

***
   
### Summary of the segments:  

```{r, echo = FALSE, Eval = TRUE, message=FALSE ,warning = FALSE}

# 2015 PopMarket Segments

customers_365$segment = 'NA'
customers_365$segment[which(customers_365$recency > 365*1)] = 'inactive'
customers_365$segment[which(customers_365$recency <= 365*1)] = 'active'
customers_365$segment[which(customers_365$segment == 'active' & customers_365$first_purchase <= 365)] = 'active new'
customers_365$segment[which(customers_365$segment == 'active' & customers_365$tl_rev < 100) ] = 'active low'
customers_365$segment[which(customers_365$segment == 'active' & customers_365$tl_rev >= 100) ] = 'active med'  
customers_365$segment[which(customers_365$segment == 'active med' & customers_365$tl_rev >= 1000) ] = 'active high'

customers_365$segment[which(customers_365$segment == 'inactive' & customers_365$tl_rev < 100)] = 'inactive low'
customers_365$segment[which(customers_365$segment == 'inactive' & customers_365$tl_rev >= 100)] = 'inactive med'
customers_365$segment[which(customers_365$segment == 'inactive med' & customers_365$tl_rev >= 1000)] = 'inactive high'
customers_365$segment  = factor(x = customers_365$segment, levels = c('active new', 'active high','active med', 'active low',
                                                                        'inactive high', 'inactive med', 'inactive low'))

segments_365 = select(customers_365, segment, tl_rev, Rev_365 )%>%
                        group_by(segment)%>%
                        summarize(Customers = n(),
                        PercOfTlCustomers = round(Customers/length(customers_365$segment),2),
                        RevTD = sum(tl_rev),
                        Rev365  = sum(Rev_365),
                        PercOfTlRev365 = round(sum(Rev_365)/sum(customers_365$Rev_365),2))

                        
                        
#print(segments_2015[,1:3])

```

```{r kable, eval=TRUE, echo=FALSE, results= "asis"}
library(knitr)
print(kable(segments_365, col.names = c('Segments','Customers','Perc of Cust','Rev. LTD','Rev 2016','Perc Tl Rev 2016')))

```

##### How neat, a perfect 80/20: In 2016 80% of revenue came from exactly 20% of customers (New Active +  Active High). 52% of revenue came from just 6% of customers (Active High + Active Medium). And 32% of revenue came from the top 2% of customers (Active High).  This site has some seriously loyal high rollers. Great!


```{r, echo = FALSE,eval=TRUE, message=FALSE ,warning = FALSE}

customers_2x_365 = select(data_1, email, amount, purchase_year,days_since)%>%
        filter(days_since  > 365)%>%  # remove all purchases made mode in the last year 
        group_by(email)%>%
        summarize(avg_amount = mean(amount),
                  tl_rev = sum(amount),
                  recency = min(days_since),
                  first_purchase = max(days_since),
                  frequency = n())

customers_rev_2x_365 = select(data_1,email,amount,days_since)%>%
                       filter(days_since > 365 & days_since <= 356*2)%>%
                       group_by(email)%>%
                       summarize(Rev_2x_365 = sum(amount))

customers_2x_365 = merge(customers_2x_365,customers_rev_2x_365, all.x = TRUE, by = 'email')

customers_2x_365$Rev_2x_365[which(is.na(customers_2x_365$Rev_2x_365))] = 0


# segment 2x_365 data
customers_2x_365$segment = 'NA'
customers_2x_365$segment[which(customers_2x_365$recency > 365*2)] = 'inactive'
customers_2x_365$segment[which(customers_2x_365$recency <= 365*2)] = 'active'

customers_2x_365$segment[which(customers_2x_365$segment == 'active' & customers_2x_365$first_purchase <= 365*2)] = 'active new'
customers_2x_365$segment[which(customers_2x_365$segment == 'active' & customers_2x_365$tl_rev < 100) ] = 'active low'
customers_2x_365$segment[which(customers_2x_365$segment == 'active' & customers_2x_365$tl_rev >= 100) ] = 'active med'  ####
customers_2x_365$segment[which(customers_2x_365$segment == 'active med' & customers_2x_365$tl_rev >= 1000) ] = 'active high'

customers_2x_365$segment[which(customers_2x_365$segment == 'inactive' & customers_2x_365$tl_rev < 100)] = 'inactive low'
customers_2x_365$segment[which(customers_2x_365$segment == 'inactive' & customers_2x_365$tl_rev >= 100)] = 'inactive med'
customers_2x_365$segment[which(customers_2x_365$segment == 'inactive med' & customers_2x_365$tl_rev >= 1000)] = 'inactive high'

customers_2x_365$segment  = factor(x = customers_2x_365$segment, levels = c('active new', 'active high','active med', 'active low',
                                                                        'inactive high', 'inactive med', 'inactive low'))

segments_2x_365 = select(customers_2x_365, segment, tl_rev,Rev_2x_365)%>%
        group_by(segment)%>%
        summarize(Customers = n(),
                  PercOfTotal = round(Customers/length(customers_2x_365$segment),2),
                  Rev = sum(tl_rev),
                  Rev_2x_365 = sum(Rev_2x_365),
                  PercOfTlRev2x_365 = round(Rev_2x_365/sum(customers_2x_365$Rev_2x_365),2)
                  )

# 2013 Customer Segments i.e. excluding all purchases made up until a year ago (then same analysis as above)

customers_3x_365 = select(data_1, email, amount, purchase_year,days_since)%>%
        filter(days_since  > 365*2)%>%  # remove all purchases made mode in the last 2 years
        group_by(email)%>%
        summarize(avg_amount = mean(amount),
                  tl_rev = sum(amount),
                  recency = min(days_since),
                  first_purchase = max(days_since),
                  frequency = n())

customer_rev_3x_365 = select(data_1,email,amount,days_since)%>%
                    filter(days_since > 365*2 & days_since <= 356*3)%>%
                    group_by(email)%>%
                    summarize(Rev_3x_365 = sum(amount))

customers_3x_365 = merge(customers_3x_365,customer_rev_3x_365, all.x = TRUE, by = 'email')
customers_3x_365$Rev_3x_365[which(is.na(customers_3x_365$Rev_3x_365))] = 0

# segment 3x_365 data
customers_3x_365$segment = 'NA'
customers_3x_365$segment[which(customers_3x_365$recency > 365*3)] = 'inactive'
customers_3x_365$segment[which(customers_3x_365$recency <= 365*3)] = 'active'
#table(customers_3x_365$segment)

customers_3x_365$segment[which(customers_3x_365$segment == 'active' & customers_3x_365$first_purchase < 365*3)] = 'active new'
customers_3x_365$segment[which(customers_3x_365$segment == 'active' & customers_3x_365$tl_rev < 100) ] = 'active low'
customers_3x_365$segment[which(customers_3x_365$segment == 'active' & customers_3x_365$tl_rev >= 100) ] = 'active med'  ####
customers_3x_365$segment[which(customers_3x_365$segment == 'active med' & customers_3x_365$tl_rev >= 1000) ] = 'active high'

customers_3x_365$segment[which(customers_3x_365$segment == 'inactive' & customers_3x_365$tl_rev < 100)] = 'inactive low'
customers_3x_365$segment[which(customers_3x_365$segment == 'inactive' & customers_3x_365$tl_rev >= 100)] = 'inactive med'
customers_3x_365$segment[which(customers_3x_365$segment == 'inactive med' & customers_3x_365$tl_rev >= 1000)] = 'inactive high'

customers_3x_365$segment  = factor(x = customers_3x_365$segment, levels = c('active new', 'active high','active med', 'active low',
                                                                        'inactive high', 'inactive med', 'inactive low'))

segments_3x_365 = select(customers_3x_365, segment, tl_rev,Rev_3x_365)%>%
        group_by(segment)%>%
        summarize(Customers = n(),
                  PercOfTlCust = round(Customers/length(customers_3x_365$segment),2),
                  Rev = sum(tl_rev),
                  Rev_3x_365 = sum(Rev_3x_365),
                  PercOfTlRev3x_365 = round(Rev_3x_365/sum(customers_3x_365$Rev_3x_365),2)
                  )
```
&nbsp;

***

### Here is how the customer segments changed over time:

```{r,echo=FALSE, eval=TRUE, message=FALSE,warning=FALSE}
segments_year = cbind(segments_3x_365,segments_2x_365,segments_365)
segments_year = cbind(segments_3x_365,segments_2x_365[,2:6],segments_365[,2:6])

```

```{r,echo=FALSE, eval=TRUE,message=FALSE,warning=FALSE}
# make table to compare no of customers per segments per year
segments_customers = segments_year[,c(1,2,7,12)]
colnames(segments_customers) = c('Segments','2014','2015','2016')
#segments_customers 
segments_customers_long = melt(segments_customers, value.name  = 'Customers')
colnames(segments_customers_long) <- c('Segment','Year','No_of_Customers')

# plot no of customers per segment per year
plot_seg = ggplot(segments_customers_long,aes(Year, No_of_Customers))
plot_seg + geom_point() + facet_grid(.~ Segment) + ggtitle("Number of customers per segmnet over the last three years\n") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ylab("Number of customers\n")
```

##### Active New customers more than doubled last year. Active High/Med/Low segments stayed almost flat. So customer acquisition efforts are paying off and customer retention is working. The challenge will be to retain these new active customers, and to convert them to higher priced offers.
&nbsp;


### Here is how revenue per segment stacks up, over time:
```{r,echo=FALSE, eval=TRUE,message=FALSE,warning=FALSE}
# make table to compare yearly REVENUE per segments per year
segments_rev = segments_year[,c(1,5,10,15)]
colnames(segments_rev) = c('Segments','2014','2015','2016')
segments_rev_long = melt(segments_rev, value.name  = 'Customers')
colnames(segments_rev_long) <- c('Segment','Year','Revenue')
```



```{r,echo=FALSE, eval=TRUE,message=FALSE,warning=FALSE}

plot_seg_rev = ggplot(segments_rev_long, aes(Year, Revenue,fill = Segment)) +  geom_bar(stat = 'identity') + ggtitle('Revenue by Customer Segment\n')
plot_seg_rev + ylab("Revenue\n") + xlab("Year\n")
```

##### New Active customers drove the increase in revenue. 

```{r,echo=FALSE, eval=TRUE,message=FALSE,warning=FALSE}
# make table to compare perc of yearly revenue by segment
segments_rev_perc = segments_year[c(1,6,11,16)]
colnames(segments_rev_perc) = c('Segment','2014','2015','2016')
seg_rev_perc_long = melt(segments_rev_perc,value.name = 'Perc_of_Yearly_Rev')
colnames(seg_rev_perc_long) <- c('Segment','Year','Rev_Perc')
```
 

```{r,echo=FALSE, eval=TRUE,message=FALSE,warning=FALSE}
#plot perc of yearly revenue by segment  - bar chart
#plot_seg_rev_perc = ggplot(seg_rev_perc_long, aes(Year, Rev_Perc,fill = Segment)) +  geom_bar(stat #= 'identity') 
#plot_seg_rev_perc + ggtitle('Revenue per segment\n (As Percentage of Total)\n') +
#ylab('Revenue as perc. of total')
```
# &nbsp;

***

## What's the value of the current data base? 
##### This isn't the same as Customer Life Time Value (CLV). CLV tells us how much a customer spends on average in her lifetime. That's very usefull to determine how much can we spend to acquire a new customer. Here we're asking how much more revenue can we expect from the customers in the data base. 


```{r,echo=FALSE, eval=TRUE,message=FALSE,warning=FALSE}

#join with table of all customers in each segment for each year
#actual = merge(customers_2015,rev_2015, all.x = TRUE, by = 'email')
#actual = merge(actual,rev_2014, all.x = TRUE, by = 'email')
#actual = merge(actual,rev_2013, all.x = TRUE, by = 'email')
#actual$rev_2015[is.na(actual$rev_2015)] = 0
#actual$rev_2014[is.na(actual$rev_2014)] = 0
#actual$rev_2013[is.na(actual$rev_2013)] = 0
#summary(actual)
#head(actual)

```

***

###  Let's make a Transition Matrix
##### It shows the probabilities of customers changing segments between 2015 and 2016, e.g. how many "Active High" customers in 2015 were also Active High customers in 2016? etc. (the answer is 67%, not bad!)

```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
new_data = merge(x = customers_2x_365, y = customers_365, by = 'email', all.x = TRUE)
transition = table(new_data$segment.x, new_data$segment.y)
transition =  round(transition / rowSums(transition),2)
kable(transition)
```
***
&nbsp;

### Let's quickly visualize where last year's New Active customers ended up: 

```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
trans = data.frame(transition)
new_active_trans = trans[which(trans$Var1 == 'active new'),]
new_active_trans = mutate(new_active_trans[-1,],perc = Freq/sum(Freq))
ggplot(new_active_trans, aes(Var2, perc)) + geom_bar(stat ='identity') + 
        ggtitle("New Active Customers in 2015 transitioned to the following segments in 2016:") + ylab('Percentage of total "New Active" customers\n') +
        xlab('Segments')

```

#### 22% of New Active customers are still Active the next year. Most of them are in the Active Medium segment. Curious to see what next year will look like...
&nbsp;

***

### How do we forecast the size of each segment over the next 5 years?

##### Let's assume customers will continue to transition from segment to segment in the same proportions as the did from 2015 to 2016. That way we can mulitply this year's segments by the transition matrix to predict next year's segments. Then we'll multiply next year's (forecasted) segments by the same transition matrix to the get the following year. And so on.
&nbsp;


```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# initialize a matrix with the number of customers in each segment today and after 10 periods

segments = matrix(nrow = 7, ncol = 6)
segments[,1] = table(customers_365$segment)
colnames(segments) = 2016:2021
rownames(segments) = levels(customers_365$segment)
#dim(segments)
#segments[,1]


# compute for every period

for (i in 2:6) {
        segments[,i] =  segments[,i-1] %*% transition
}

segments[,2] = segments[,1] %*% transition
#segments[,1]%*% transition
round(segments)
```

***

### Now we can forecast revenue per segment for the next 5 years
#####(assuming that, on average, revenue per segment stays the same)

```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# average rev per customer in each segment in 2015

rev_2016_segment = select(customers_365, Rev_365, segment)%>%
                   group_by(segment)%>%
                   summarize(avg_rev = round(mean(Rev_365),0))

#print(rev_2015_segment)

yearly_revenue = rev_2016_segment$avg_rev
revenue_per_segment = round(yearly_revenue * segments,0)
#revenue_per_segment
```
&nbsp;

***

```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#Compute yearly revenue

yearly_revenue = colSums(revenue_per_segment)
#print(round(yearly_revenue))
yearly_rev_seg_long = melt(revenue_per_segment)
colnames(yearly_rev_seg_long) = c('Segment','Year','Revenue')
#yearly_rev_seg_long
ggplot(yearly_rev_seg_long, aes(Year, Revenue, fill=Segment)) + geom_bar(stat = 'identity') + ggtitle('Revenue Forecast by Segment\n')
```

***

```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#Compute cumulative revenue
# yearly_revenue
cumulative_revenue = cumsum(yearly_revenue)
#print(round(cumulative_revenue))
cume_rev = data.frame(cumulative_revenue)
cume_rev$Year = row.names(cume_rev)
row.names(cume_rev) = NULL
ggplot(cume_rev, aes(Year, cumulative_revenue)) + geom_bar(stat = 'identity') + ggtitle('Cumulative Revenue Projected\n')

```

***

```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#create discount factor
discount_rate = .1
discount = 1 / (1 + discount_rate) ^ ((1:5)-1)
#discount
```

```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# compute yearly discounted revenue

#yearly_revenue
disc_yearly_revenue = discount * yearly_revenue
#print(round(disc_yearly_revenue))

```

```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# compute discounted cumulative revenue

disc_cumulative_revenue = cumsum(disc_yearly_revenue)
disc_cume_rev = data.frame(disc_cumulative_revenue)
disc_cume_rev$Year = row.names(disc_cume_rev)
row.names(disc_cume_rev) = NULL
colnames(disc_cume_rev) = c("Cume_Rev", "Year")
ggplot(disc_cume_rev, aes(Year, Cume_Rev)) + geom_bar(stat = 'identity') + ggtitle('Present Value of Cumulative Revenue\n Discounted at 10%\n') + ylab("Cumulative Revenue")
```

#### Total net present value of the data base in 2020 is:
```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# what is the data base worth?
cust_value = disc_cumulative_revenue[6] - disc_cumulative_revenue[1]
cust_value = prettyNum(cust_value, big.mark = ",")
cust_value_1 = as.data.frame(cust_value, row.names = 'Net Present Value')
names(cust_value_1) = c("2020")
kable(cust_value_1)


```

### And let's add the Customer Life Time Value
```{r,echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# Customer Life Time value
LTV = prettyNum((disc_cumulative_revenue[6] - disc_cumulative_revenue[1])/dim(customers_365)[1],big.mark = ",", digits = 4)

value_table = data.frame(LTV, cust_value)
colnames(value_table) = c("Customer Life Time Value", "Total Net Present Value of Data Base")
kable(value_table)
```




